---
title: "EUNIS Classification Systems"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(eunis.habitats)
library(dplyr)
```

EUNIS habitats are provided as the tidy data set `eunis_habitats`, each row
corresponding to a habitat at varying levels of description.

```{r}
eunis_habitats
```

## EUNIS four classifications

The `eunis_habitats` data set comprises four habitat classifications:

1. EUNIS classification from 2007, revised in 2012.
2. EUNIS marine classification from 2019.
3. EUNIS marine classification from 2022.
4. EUNIS terrestrial classification from 2021.

The column `classification` distinguishes which is which:

```{r}
dplyr::distinct(eunis_habitats, classification)
```

For example, to access the level 1 marine habitats classified
according to EUNIS revision of 2022 (`"EUNIS_M_2022"`):

```{r}
dplyr::filter(eunis_habitats, classification == "EUNIS_M_2022", level == 1L)
```

And to list ice habitats (level 2):

```{r}
dplyr::filter(eunis_habitats,
              classification == "EUNIS_M_2022",
              group == "ice",
              level == 2L) |>
  dplyr::select("code", "name")
```

